---
title: "pakistan"
output:
  md_document:
    variant: gfm # github format
---

```{r open-libaries}
library("readr")
library("readxl")
library("tidyverse")
```

```{r}
excel_data <- read_excel("data/dsat_through_2024.xlsx", sheet = "tblAggregation_Attacks_QTA")
write_csv(excel_data, "data/dsat_research.csv")
```


REMEMBER TO RECREATE EVERYTHING!!! perhaps also make a flow chart... 

But at any rate:

Explain strategic logic of suicide terrorism.

Clean data.

Then: visualizations:

First: a flow chart on what the current thingies are

1. TTP vs BLA over time
2. Geographic data of BLA attacks
3. textual analysis of both claim texts and comparison
4. (probably earlier) Pakistan attacks over time
5. BLA attacks against Chinese over time
6. Perhaps Chinese-specific attacks not in China
7. Final flow chart of potential revised theory
8. MAYBE EVEN a death chart -- showing the IMPORTANCE of understanding these attacks

```{r creation-dsat-csv}
dsat <- read_csv("data/dsat_research.csv")
```

```{r pakistan-history}
pakistan_history <- dsat %>%
  filter(AimPointCountry_Agg == "Pakistan")
chinese_attacked_pakistan <- pakistan_history %>%
  filter(TT_Nationality == "Chinese")
```

```{r total-attacks-2023}
attacks_2023 <- dsat %>%
  filter(AttackYear == 2023, AimPointCountry_Agg == "Pakistan") 
attacks_2024 <- dsat %>%
  filter(AttackYear == 2024, AimPointCountry_Agg == "Pakistan")
```

```{r total-attacks-against-Chinese}
chinese_attacked_outside_china <- dsat %>%
  filter(AimPointCountry_Agg != "China", TT_Nationality == "Chinese") 
ggplot(chinese_attacked_outside_china, aes(x = AimPointCountry_Agg, fill = AimPointCountry_Agg)) +
  geom_bar() +
  labs(
    title = "Number of Attacks Against Chinese",
    x = "Country Attacked"
  )
```

```{r balochistan-liberation-army}
bla_attacks <- dsat %>%
  filter(Claimed_Agg2 == "Balochistan Liberation Army")

ggplot(bla_attacks, aes(x = AttackYear, fill = TT_Nationality)) +
  geom_bar() + 
  labs(
    title = "History of Balochistan Liberation Army Attacks",
    x = "Year of Attack", y = "Number of Attacks"
  ) #plot against region?
```


```{r pakistan-attacks-over-time}
pakistan_yearly_summary <- pakistan_history %>%
  group_by(AttackYear) %>%
  summarize(attack = n())
# visualization
ggplot(pakistan_yearly_summary, aes(x = AttackYear, y = attack)) +
  geom_line() + 
  labs(
    title = "Attacks per year in Pakistan, 1995-2024",
    x = "Year of Attack", y = "Quantity of Attacks"
  ) +
  theme_bw()
```

```{r pakistan-aggregate-attacker}
pakistan_aggregate_attacker <- pakistan_history %>%
  group_by(AttackYear, Claimed_Agg2) %>%
  summarize(attack = n())
```


